---
title: "Mutivariate_ts_HBO"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(nnfor)
library(forecast)
library(vars)
library(tswge)
library(RSNNS)

#download data
library(readr)  # for read_csv
library(knitr)  # for kable
myfile <- "https://raw.githubusercontent.com/dclark18/hbo_spike_analysis/main/conversion_date_hour.csv"

imp <- read_csv(myfile)
imp <- imp[1:1416,]

#imp$Conversions[is.na(imp$Conversions)] <- 0
#imp$Impressions[is.na(imp$Impressions)] <- 0
```

In this study we will be using mutivariate approaches to better understand the impact of tv impressions from HBO on other variables related to advertising conversion, viewership, and Search Engagement. 

## Step 1
Plot the data. Data runs from 9/15 - 11/15 with points set for the hourly level. 

```{r regress, include=TRUE}

plotts.sample.wge(imp$Impressions)
plotts.sample.wge(imp$Conversions)
```
Since neither show a good sense of seasonality, let's difference both impressions and conversions

```{r diff, include=TRUE}
#impdif <- imp
imp$Impressions <- diff(imp[1:1417,]$Impressions,1)
imp$Conversions <- diff(imp[1:1417,]$Conversions,1)
plot.ts(imp$Impressions, main = 'different variance')
plot.ts(imp$Conversions, main = 'different variance')

```

Both are showing a lack of visual stationarity with a large fluctuation happening around hte middle of the data set with a tailing off in the more recent window. The autocorrelations for the impressions does imply a bit of a 24 hour cycle happening, but not super apparent at this level. Conversions are much less so. 

```{r fit, include=TRUE}
imp$Impressions <- imp$Impressions / 100

ksfit = lm(Conversions~Impressions, data = imp)
aic.wge(ksfit$residuals, p=0:30, q=0) #AIC says use P 29
fit = arima(imp$Conversions, order = c(28,0,0), xreg=cbind(imp[,2:3]))
#fit = arima(imp$Conversions, order = c(28,0,0), xreg=xreg, method="CSS")

fit
```

Explore the existence of Cross Correlations between impressions and correlations. 

```{r ccf, include = TRUE}
ccf(imp$Conversions, imp$Impressions)
```

Looks like there's a lag of 24 on the hourly data. At an ACF of over 0.5.

Let's now open the date file to see what the lag is between impressions and conversions grouped by date. 

```{r dategroup, include = FALSE}
#download data
library(readr)  # for read_csv
library(knitr)  # for kable
myfile <- "https://raw.githubusercontent.com/dclark18/hbo_spike_analysis/main/conversionsimpressionsbydate.csv"

df <- read_csv(myfile)

df$Conversions[is.na(df$Conversions)] <- 0
```


Now let's perform a CCF to see how the lags shape out

```{r ccf2, include=TRUE}

ccf(df$Conversions, imp$Impressions)

```